---
title: "HW6"
author: "jgn2108"
date: "`r Sys.Date()`"
output: github_document
---

## Set up
```{r setup, include=FALSE}
library(readr)
library(tidyverse)
library(skimr)
library(dplyr)
library(broom)
library(purrr)
library(broom)
library(ggplot2)
library(tidyr)
library(stringr)
library(boot)
library(modelr)
library(nlme)
library(mgcv)
```

## Problem 1

Loading data: Washington Post homicide data
```{r}
url <- "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

# Read the CSV file into a data frame
homicide_data <- read_csv(url)

# View the first few rows of the data
head(homicide_data)
```
Reformat reported_date
```{r}
# Convert numeric date to Date object
homicide_data$reported_date <- as.Date(as.character(homicide_data$reported_date), format = "%Y%m%d")

# Format the date as MM/DD/YYYY
homicide_data$reported_date <- format(homicide_data$reported_date, "%m/%d/%Y")
```
Create first variable
```{r}
# Create city_state variable
homicide_data <- mutate(homicide_data, city_state = paste(city, state, sep = ", "))
homicide_data
```

Create a binary factor variable re: disposition
```{r}
homicide_data <- homicide_data %>%
  mutate(disposition = relevel(factor(disposition, levels = c("Closed by arrest", "Closed without arrest")),
                               ref = "Closed by arrest"))
str(homicide_data)
```

```{r}
homicide_data <- homicide_data %>%
  mutate(disposition2 = factor(ifelse(disposition == "Closed by arrest", "solved", "unsolved"),
                               levels = c("solved", "unsolved"),
                               exclude = NULL))
homicide_data
```

Omit rows with the following city_state:"Dallas, TX"; "Phoenix, AZ"; "Kansas City, MO"; and "Tulsa, AL" 
```{r}
homicide_data <- homicide_data %>%
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
homicide_data #from 52179 observations, down to 48507
```

Make victim_age numeric
```{r}
homicide_data <- homicide_data %>%
  mutate(victim_age = as.numeric(victim_age))
str(homicide_data)
```

Make victim_race a factor variable
```{r}
homicide_data <- homicide_data %>%
  mutate(victim_race = factor(victim_race, 
                              levels = c("Hispanic", "White", "Black", "Asian", "Other"),
                              labels = c(1, 2, 3, 4, 5),
                              exclude = NULL))
str(homicide_data)
```

Filter out all victim_race that are not "White" or "Black"
```{r}
homicide_data_filtered <- homicide_data %>%
  filter(victim_race %in% c(2, 3))
str(homicide_data_filtered) #from 52179 rows, now n=39693
```

Fit a logistic regression model, outcome=disposition2
```{r}
model <- glm(disposition2 ~ victim_age + victim_sex + victim_race, data = homicide_data_filtered, family = "binomial")
summary(model) #model summary

```

Now store it as an R object and get estimates and CIs for adjusted OR btw male vs. female victims
```{r}
save(model, file = "logistic_regression_model.RData") # Save the output of glm as an R object

# Apply broom::tidy to the model
tidy_model <- broom::tidy(model)
print(tidy_model)

# Extract the estimate and CI for the adjusted OR comparing male vs. female victims
odds_ratio_estimate <- tidy_model %>%
  filter(term == "victim_sexMale") %>%
  select(estimate)

odds_ratio_ci <- tidy_model %>%
  filter(term == "victim_sexMale") %>%
  select(matches("conf\\.low"), matches("conf\\.high"))


odds_ratio_estimate
odds_ratio_ci
```

Now do LR by city within a "tidy" worklow
```{r}
citywise_results <- homicide_data_filtered %>%
  group_by(city_state) %>%
  nest() %>%
  mutate(
    model = map(data, ~ glm(disposition2 ~ victim_age + victim_sex + victim_race, data = ., family = "binomial", control = list(maxit = 1000))),
    tidy_model = map(model, tidy)
  ) %>% unnest(tidy_model)

citywise_results
```
Check column names
```{r}
names(citywise_results)
```


Plot this
```{r}
# Create a plot
ggplot(citywise_results, aes(x = reorder(city_state, estimate), y = estimate, ymin = estimate - 1.96 * std.error, ymax = estimate + 1.96 * std.error)) +
  geom_point(position = position_dodge(width = 0.2)) +
  geom_errorbar(position = position_dodge(width = 0.2), width = 0.2) +
  labs(title = "Estimated Odds Ratios and CIs for Each City",
       x = "City",
       y = "Estimated Odds Ratio") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Problem 2

Get Central Park weather data
```{r}
file_path <- "/Users/jgn/Desktop/P8105/HW6/nynoaadat.csv"

weather_df <- read_csv(file = file_path) %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10
  ) %>%
  select(name, id, everything())
```

Do a linear regression first
```{r}
linear_regression <- function(data, indices) {
  sample_data <- data[indices, ]
  model <- lm(tmax ~ tmin + prcp, data = sample_data) #tmax, tmin, and prcp
  r_squared <- summary(model)$r.squared #r_hat squared
  beta1_beta2_log <- log(coef(model)[2] * coef(model)[3]) #log (beta_hat_1 * beta_hat_2)
  c(r_squared, beta1_beta2_log)
}
```

Use broom::glance function, and cause of error messages, check for NaNs in the results
```{r}
linear_regression <- function(data) {
  model <- lm(tmax ~ tmin + prcp, data = data) # tmax, tmin, and prcp
  glance_result <- broom::glance(model)
  tidy_result <- broom::tidy(model)

  # Check for NaNs in the results
  if (any(is.na(glance_result$r.squared)) || any(is.na(tidy_result$estimate[2:3]))) {
    warning("NaNs produced in linear regression. Returning NA values.")
    return(c(NA, NA))
  }

  r_squared <- glance_result$r.squared
  beta1_beta2_log <- log(tidy_result$estimate[2] * tidy_result$estimate[3])

  c(r_squared, beta1_beta2_log)
}
linear_regression
```

```{r}

```

Now bootstrapping
```{r, include=FALSE}
set.seed(123)  # Set seed
#bootstrap_results <- boot(data = weather_df, statistic = linear_regression, R = 50) NOT WORKING
bootstrap_results <- lapply(1:5000, function(i) {
  indices <- sample(nrow(weather_df), replace = TRUE)
  sample_data <- weather_df[indices, ]
  linear_regression(sample_data)
})
```

```{r}
set.seed(123) 
bootstrap_results <- matrix(0, nrow = 5000, ncol = 2)

for (i in 1:5000) {
  indices <- sample(nrow(weather_df), replace = TRUE)
  sample_data <- weather_df[indices, ]
  bootstrap_results[i, ] <- linear_regression(sample_data)
}
```


```{r}
weather_df =
  crossv_mc(child_growth, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))


weather_df = 
  crossv_mc(nonlin_df, 100)
```


